Metropolitan Statistical Area Evaluation

### 2022-11-10 src/demo_data_wrangling.Rmd
new list of MSAs/Cities with updated population sizeof 500,000

```{r population growth data wrangling}
# read in the data MSA population data from Census
msa_pop_2021_data <- read_csv(here("data","raw", "msa_2021_alldata.csv")) %>% 
  clean_names() %>% # data wrangling to make column headers in lower_snake_case
  filter(lsad == "Metropolitan Statistical Area") %>% # select MSA cities
  select("cbsa", "name", "popestimate2020", "popestimate2021", "residual2020", "residual2021") %>% # select data 
  filter(popestimate2021 >= 300000) %>% 
  separate(col = "name",
           into = c("MSA", "state"), # split city and state data
           sep = ", ") %>% 
  mutate(pop_percent_change = (popestimate2021-popestimate2020)/popestimate2021 * 100)  # add population % change column

>>>>

```{r population growth data wrangling}
# read in the data MSA population data from Census
msa_pop_2021_data <- read_csv(here("data","raw", "msa_2021_alldata.csv")) %>% 
  clean_names() %>% # data wrangling to make column headers in lower_snake_case
  filter(lsad == "Metropolitan Statistical Area") %>% # select MSA cities
  select("cbsa", "name", "popestimate2020", "popestimate2021", "residual2020", "residual2021") %>% # select data 
  filter(popestimate2021 >= 500000) %>% 
  separate(col = "name",
           into = c("MSA", "state"), # split city and state data
           sep = ", ") %>% 
  mutate(pop_percent_change = (popestimate2021-popestimate2020)/popestimate2021 * 100)  # add population % change column
